### 2017-12-22 papers/cua.tex
cua: use matrix mode to draw tasks

\newcommand\task[3]{
\node (#1) [task] at (#2) {#1};

\IfSubStr{#3}{l}{
\foreach \i in {-8,...,8}%
{
  \draw[xshift=-5em, ultra thick] (#2) +(0,0.2 * \i) -- +(0.2,0.2 * \i) coordinate (#1 Port \i);

@@

\IfSubStr{#3}{r}{
\foreach \i in {-8,...,8}%
{
  \draw[xshift=5em, ultra thick] (#2) +(-0.2,0.2 * \i) -- +(0,0.2 * \i) coordinate (#1 Port \i);

}
}{}
}

@@

\task{Task 1}{0,0}{r}
\task{Task 2}{15 em,0}{l}
\task{Task 3}{0,-15 em}{r}

\node (message) [message] at (0,-1 em) {Message 1};
\node (message2) [message] at (15 em, -1 em) {Message 1};
\node (message2a) [message] at (16 em, -2.5 em) {Message 2};
\node (message3) [message] at (0, -15 em) {Message 2};

\draw [color=violet, thick, ->] (node cs:name=message,angle=20) -- +(.3,0) |- (Task 1 Port 3) node [midway, anchor=south, color=black] {27} -- (Task 2 Port 3)
    -- +(.3,0) node [near end, anchor=south, color=black] {52} |- (node cs:name=message2, angle=160);

>>>>

\newcommand\task[4]{
\node (#1) [matrix, task] at (#2) {\node {#1}; #4

\IfSubStr{#3}{l}{
\foreach \i in {-8,...,8}%
{
  \draw[xshift=-5em, ultra thick] (0,0.2 * \i) -- (0.2,0.2 * \i) coordinate (#1 Port \i);

@@

\IfSubStr{#3}{r}{
\foreach \i in {-8,...,8}%
{
  \draw[xshift=5em, ultra thick] (-0.2,0.2 * \i) -- (0,0.2 * \i) coordinate (#1 Port \i);

\\};
}

@@

\task{Task 1}{0,0}{r}{
\node (message1) [message] {Message 1};
}
\task{Task 2}{15 em,0}{l}{
\node (message2) [message] {Message 1};
\node (message2a) [message] at (1 em, -2 em) {Message 2};
}
\task{Task 3}{0,-15 em}{r}{
\node (message3) [message] {Message 2};
}

\draw [color=violet, thick, ->] (node cs:name=message1,angle=20) -- +(.3,0) |- (Task 1 Port 3) node [midway, anchor=south, color=black] {27} -- (Task 2 Port 3)
    -- +(.3,0) node [near end, anchor=south, color=black] {52} |- (node cs:name=message2, angle=160);
